A Classical Analog of Quantum Interaction-Free Measurement

### 2015-07-17 ms/ifm.tex
editing

\begin{abstract}
Interaction-free measurement is usually discussed in quantum language and
refers to phenomena such as the presence of a photon absorber being
inferred without it actually absorbing any photons.  Here we make the
simple observation that there is an
exactly analogous situation in classical mechanics: If one has
a pair of identical coupled oscillators A \& B, and A is set in motion,
then one will see the strength of the oscillation of A slowly decrease
with time, and over longer times the energy will periodically `slosh' back
and forth between the two systems.  But if instead oscillator B is damped -- so
it is able to {\em absorb\/} energy -- the rate of decrease of the
energy in oscillator A will be suppressed.   
Thus one can infer the ability of oscillator B to 
absorb energy by observing the behaviour of oscillator A without, in
the limit that the damping is strong, there actually being any
energy absorbed.
% We review the physics and its realization in interferometric
% experiments.  We then consider a simple classical system: two coupled
% oscillators, one of which is damped; the energy dissipation can be
% made arbitrarily small by making the damping large enough.  The
% phenomenon can be considered analogous to interaction-free
% measurement.
\end{abstract}

@@

In this paper, we relate the above simple picture on the one hand to
the standard description of interaction-free measurement in terms of
an interferometric setup, and on the other hand to a classical system
of coupled oscillators.

>>>>

\begin{abstract}
Interaction-free measurement generally refers to quantum phenomena
such as the presence of a photon absorber being inferred without it
actually absorbing any photons.  Here we make the simple observation
that there is an analogous situation in classical mechanics: two
coupled oscillators, one of which is damped; the energy dissipation
can be made arbitrarily small by making the damping large enough, thus
revealing the presence of the damper despite arbitrarily low energy
dissipation.
\end{abstract}

@@

In this paper, we argue that interaction-free measurement need not be
quantum at all.  Rather, the characteristics features of (a)~an
amplitude that cycles between two states, but (b)~an absorber can
block this cycling, thus revealing its presence, but without actually
absorbing any energy, can also appear in classical systems.  If one
has a pair of identical coupled oscillators $x$ and $y$, and $x$ is
set in motion, one will see the strength of the oscillation of $x$
slowly decrease with time, and over longer times the energy will
periodically `slosh' back and forth between the two systems.  But if
instead oscillator $y$ is damped --- so it is able to {\em absorb\/}
energy --- the rate of decrease of the energy in oscillator $x$ will
be suppressed.  Thus one can infer the ability of oscillator $y$ to
absorb energy by observing the behaviour of oscillator $x$ without, in
the limit that the damping is strong, there actually being any energy
absorbed.
